---
title: "Rmarkdown with R code"
author: Qi Wang
output: 
  html_document: 
    toc: yes
    number_sections: yes
date: "2023-10-23"
---

Create a code chunk to write R code and present code and output. Rmarkdown also can present other languages, e.g., Python

1. Use `install.packages()` to install packages in R. Use `library()` to tell R to load this pacakge. (Use "\`.\`" to indicate functions in the output).
```{r warning = FALSE}
# Install packages by using install.packages() function
install.packages("datasets")
# Load R package via library() function
library(datasets)
# Use data() function to allow users to load datasets from packages for use in their examples
data(airquality)
```

2. Check the dataset `airquality`.
```{r warning = FALSE}
# Check the first six rows of the dataset airqquality
head(airquality)
# Check the last six rows of the dataset airqquality
tail(airquality)
```

3. Check sample size and the number of variables of the dataset
```{r warning = FALSE}
# Check sample size
nrow(airquality)
# Check the number of variables
ncol(airquality)
```

4. Check NA in the dataset.
```{r warning = FALSE, results='hide'}
# Check NAs in the dataset
is.na(airquality)
```
5. Calculate the number of NAs 
```{r warning = FALSE}
# Check NAs in the dataset
sum(is.na(airquality))
```
6. Delete observations which include NAs.
```{r warning = FALSE}
# Remove NAs from the dataset
air.complete <- airquality[!is.na(airquality), ]
head(air.complete)
```

7. Draw a plot with the complete data
```{r warning = FALSE}
# Check NAs in the dataset
plot(air.complete$Wind, air.complete$Solar.R, main = "Practice of Airquality",
    xlab = "wind", ylab = "solar")
```
